A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-12 dl-paper.tex
Fix 30-31

Notice that by~\eqref{eq:conj-h-x} $[h'] = [h'']$, where $h'' = h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\beta(b_0).$
From~\cref{P0-conj-invariant} and \cref{SR:additivity} we obtain that
\begin{multline*} p(g',h'',u(1-am)) = x_{\beta}(-Xf) \cdot \left(S_\alpha(a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\right)^{x_\beta(b_0)} \in \\ \in x_{\beta}(-Xf) \cdot P_\alpha(\tfrac{m}{1-am})^{x_\beta(b_0)} \subseteq P_\alpha(\tfrac{m}{1-am}).\end{multline*}
Thus, we can invoke ~\eqref{T_1}--\eqref{T_leq0} once again and can continue~\eqref{R3leq0-computation} as follows:
\begin{equation} \label{R3leq0-computation2} \ldots = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0)], u \right) = \left(g, [h], u\right), \end{equation}
where in the last equality we use the following computation:
\begin{equation} \nonumber
 h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0) = h \cdot h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(a(1-am)X^{-1}\right),\ x_\beta(b_0)\right] = h \cdot h_\alpha^{-1}(1-am). \end{equation}
The assertion of the lemma now follows from~\eqref{R3leq0-computation}--\eqref{R3leq0-computation2}. \end{proof}

@@

\begin{lemma} \label{R3_1_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R3}_{1,1}^{\angle}$. \end{lemma}
\begin{proof}
Let $a, b \in A$ and $\alpha$, $\beta$ be a pair of roots forming a sharp angle. Set $\epsilon = N_{\alpha,-\beta}$. From~\cref{K-a-b} and the proof of the first part of~\cref{lem:orbit-action} it follows that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\beta}(m')\text{ for some }m,m' \in M.\]
From~\eqref{T_1} we obtain that
\begin{multline} \label{R3_1_1-computation}
 T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, [h], u\right) = \\
 = T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)\right],\ u(1 + am)\right) = \\ 
 = T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h'\right],\ u(1 + am)\right),
 \end{multline}
where $h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am').$
Notice that by~\cref{SR:sharp}
\[ p(x_\alpha(aX^{-1})\cdot g, h', u(1 + am)) = S_\alpha(p(g, h, u) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \in P_\beta(\tfrac{m'}{1+am}), \]
therefore we can invoke~\eqref{T_1} once again and can continue~\eqref{R3_1_1-computation} as follows:
\begin{equation}\label{R3_1_1-computation2} \ldots = \left(x_\beta(bX^{-1}) \cdot x_\alpha(aX^{-1}) \cdot g, \left[h' \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm'}{1+am}}\right)\right], u(1 + am + bm')\right). \end{equation}
The second component of the above triple can be simplified using~\eqref{eq:conj-h-x} as follows:
\begin{multline*}
 \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right)\right] = \\
 = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right)\right] = \\
 = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am)\right] = \\
 = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right)\right].
\end{multline*}
Thus, we see that the expression in the right-hand side of~\eqref{R3_1_1-computation2} would remain unchanged if we swapped $(a,\alpha,m)$ with $(b,\beta,m')$. This implies the required assertion.
\end{proof}

@@

As before, we may assume that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m')\ttxt{ for some $m, m' \in M\].

Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that 
\begin{multline} \nonumber
[T_\beta(b),\ T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
 = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h'],\ u (1 - am) \right) = \\
 = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ u c\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u),\end{multline} 
 where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$  
  and the last equality is obtained as follows:
 \begin{multline} \nonumber
 h'' = h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \cdot x_\beta(-b) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\
 = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right). \qedhere
\end{multline}
\end{proof}

@@

This action satisfies the following additional properties.
\begin{enumerate}
 \item For any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
 \item If we consider $\St(\Phi, A[X, X\inv])$ as a set with the left multiplication action of $\St(\Phi, B)$ then the map $\overline{V} \to \St(\Phi, A[X, X\inv])$ given by $(g, [h], u) \mapsto g$ is a map of $\St(\Phi, B)$-sets.
\end{enumerate}
\end{prop}
\begin{proof} By~\cref{superfluous-relations} and Lemmas~\ref{R1_d}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined. On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} (set $t = X^{-1}$).

>>>>

Notice that by~\eqref{eq:conj-h-x} $[h'] = [h'']$, where $h'' = h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\beta(b_0).$
From~\cref{P0-conj-invariant} and \cref{SR:additivity} we obtain that
\begin{multline*} p(g',h'',u(1-am)) = x_{\beta}(-Xf) \cdot \left(S_\alpha(-a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\right)^{x_\beta(b_0)} \in \\ \in x_{\beta}(-Xf) \cdot P_\alpha(\tfrac{m}{1-am})^{x_\beta(b_0)} \subseteq P_\alpha(\tfrac{m}{1-am}).\end{multline*}
Thus, we can invoke ~\eqref{T_1}--\eqref{T_leq0} once again and can continue~\eqref{R3leq0-computation} as follows:
\begin{equation} \label{R3leq0-computation2} \ldots = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0)], u \right) = \left(g, [h], u\right), \end{equation}
where in the last equality we use the following computation:
\begin{equation} \nonumber
 h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0) = h \cdot h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(a(1-am)X^{-1}\right),\ x_\beta(b_0)\right] = h \cdot h_\alpha^{-1}(1-am). \end{equation}
The assertion of the lemma now follows from~\eqref{R3leq0-computation}--\eqref{R3leq0-computation2}. \end{proof}

@@

\begin{lemma} \label{R3_1_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R3}_{1,1}^{\angle}$. \end{lemma}
\begin{proof}
Let $a, b \in A$ and $\alpha$, $\beta$ be a pair of roots forming a sharp angle. Set $\epsilon = N_{\alpha,-\beta}$. From~\cref{K-a-b} and the proof of the first part of~\cref{lem:orbit-action} it follows that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\beta}(m')\text{ for some }m,m' \in M.\]
From~\eqref{T_1} we obtain that
\begin{multline} \label{R3_1_1-computation}
 T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, [h], u\right) = \\
 = T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)\right],\ u(1 + am)\right) = \\ 
 = T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h'\right],\ u(1 + am)\right),
 \end{multline}
where $h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am').$
Notice that by~\cref{SR:sharp}
\[ p\left(x_\alpha(aX^{-1})\cdot g, h', u(1 + am)\right) = S_\alpha(a, p(g, h, u)) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \in P_\beta(\tfrac{m'}{1+am}), \]
therefore we can invoke~\eqref{T_1} once again and can continue~\eqref{R3_1_1-computation} as follows:
\begin{equation}\label{R3_1_1-computation2} \ldots = \left(x_\beta(bX^{-1}) \cdot x_\alpha(aX^{-1}) \cdot g,\ \left[h' \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm'}{1+am}}\right)\right],\ u(1 + am + bm')\right). \end{equation}
The second component of the above triple can be simplified using~\eqref{eq:conj-h-x} as follows:
\begin{multline*}
 \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right)\right] = \\
 = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right)\right] = \\
 = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am)\right] = \\
 = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right)\right].
\end{multline*}
Thus, we see that the expression in the right-hand side of~\eqref{R3_1_1-computation2} would remain unchanged if we swapped $(a,\alpha,m)$ with $(b,\beta,m')$. This implies the required assertion.
\end{proof}

@@

As before, we may assume that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m')\text{ for some $m, m' \in M$.} \]

%Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that 
%
From~\eqref{T_1}--\eqref{T_leq0} and~\eqref{eq:conj-h-x} we obtain that
\begin{multline} \label{R2_0_1-computation}
[T_\beta(b),\ T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\beta}(b)],\ u (1 - am) \right) = \\
= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h'],\ u (1 - am) \right),
 \end{multline} 
 where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$. Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that
\begin{multline*} p\left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ h',\ u (1 - am) \right) = \\ =
 x_\beta(-b) \cdot S_\alpha(-a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc) \in P_\alpha(\tfrac{m+\epsilon bm'}{1-am}). \end{multline*}
Thus, we can continue~\eqref{R2_0_1-computation} using~\eqref{T_1}--\eqref{T_leq0}:
\begin{equation} \label{R2_0_1-computation2} \ldots = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ uc\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u), \end{equation} where the last equality is obtained via~\eqref{eq:conj-h-x} as follows:
 \begin{multline} \nonumber
 [h''] = \left[ h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \cdot x_\beta(-b) \right] = \\ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \right] = \\
 = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \right]   = \\ = \left[ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right) \right].
\end{multline}
The assertion of the lemma now follows from~\eqref{R2_0_1-computation}--\eqref{R2_0_1-computation2}.
\end{proof}

@@

This action satisfies the following additional properties.
\begin{enumerate}
 \item For any $h_1 \in \St(\Phi, A[X\inv])$ one has $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
 \item If we consider $\St(\Phi, A[X, X\inv])$ as a set with the left multiplication action of $\St(\Phi, B)$ then the map $\overline{V} \to \St(\Phi, A[X, X\inv])$ given by $(g, [h], u) \mapsto g$ is a map of $\St(\Phi, B)$-sets.
\end{enumerate}
\end{prop}
\begin{proof} By~\cref{superfluous-relations} and Lemmas~\ref{R1_d}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined. On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} (set $t = X^{-1}$).
